Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: edgb section first version done

As we stressed in Sec.~\ref{sec:remarks}, before we can draw any conclusions on
the allowed values for $\ell_{\rm GB}$ from our parameter estimation study, we
must first check whether the ``EFT''~\eqref{eq:eft_bound} and
``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
%
We verify the former in Fig.~\ref{fig:edgb_cdf}. In top (bottom) panel we shown the cumulative density function
of the $\ell_{\rm GB}$ posteriors, obtained evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or the remnant's mass ($\mathfrak{m} = M_f$, solid lines), with varying $\epsilon$.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the
cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
$\varepsilon$ for both (blue curves) $\gm = m_2$, the secondary's source
mass, and (orange curves) $\gm = M_{f}$, the remnant's source mass, without
(solid curve) and with (dashed curves) linear in spin QNM corrections. The
horizontal lines lay at 0.68 and 0.90. We see that in no situation the curves pass
through the 0.68 or 0.90 lines even at $\varepsilon = 1$. This means that no bound on $\ell_{\rm GB}$
can be placed with the event we analyzed.
}
\label{fig:edgb_cdf}
\end{figure}

>>>>

As we stressed in Sec.~\ref{sec:remarks}, before we can draw any conclusions on
the allowed values for $\ell_{\rm GB}$ from our parameter estimation study, we
must first check whether the ``EFT''~\eqref{eq:eft_bound} and
``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
%
We verify the former in Fig.~\ref{fig:edgb_cdf}. In top (bottom) panel we shown
the cumulative density function of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$.
%
For GW150914, we see that for the $N_{\rm max} = 0$ that the CDF never goes past $0.2$, regardless of the mass scale $\mathfrak{m}$,
even at $\varepsilon = 1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is never met
at a significant credilibity and thus that we cannot place a bound on $\ell_{\rm GB}$.
%
The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not change when we include spin corrections to the EdGB QNM.
%
Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our present model}.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the
cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
$\varepsilon$ for both (blue curves) $\gm = m_2$, the secondary's source
mass, and (orange curves) $\gm = M_{f}$, the remnant's source mass, without
(solid curve) and with (dashed curves) linear in spin QNM corrections. The
horizontal lines lay at 0.68 and 0.90. We see that in no situation the curves pass
through the 0.68 or 0.90 lines even at $\varepsilon = 1$. This means that no bound on $\ell_{\rm GB}$
can be placed with the events we analyzed.
}
\label{fig:edgb_cdf}
\end{figure}
